---
title: "Twitter_Sentiment"
author: "Ryan Jolicoeur"
date: "April 28, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(Quandl)
library(readr)
library(curl)
library(dplyr)
library(zoo)
library(ggplot2)
library(plotly)

api <- "ij6nAJPwMWJCbmVbEh-j"

```

## Twitter Sentiment
In this assignment we are going to be looking at average sentiment of Twitter from January 2017
through March 2018.  We are going to aggregate the data by the aggregate monthly amount. We are also going to put the high and the low sentiment by month for the date range.  
```{r Twitter Data}
twitter_sentiment <- Quandl("NS1/TWTR_US", api_key=api)

twitter_sentiment <- twitter_sentiment %>%
                      filter(Date >= '2017-01-01')

twitter_sentiment <- zoo(twitter_sentiment[,-1], 
                         order.by = as.Date(twitter_sentiment[,1], 
                         format = "%d/%m/%Y"))

twitter_sentiment  <- aggregate(twitter_sentiment, as.yearmon, mean)

twitter_sentiment  <- data.frame(Date = index(twitter_sentiment),
                                coredata(twitter_sentiment))

twitter_sentiment  <- twitter_sentiment %>% 
                        select(-contains("News"))
```

## Plotly Graph

Now that we have the data aggregated we will plot the graph data to show the high and low; as well as the average Twitter Sentiment by month to the following Plotly graph.  

```{r Plotly Graph}
p <- plot_ly(twitter_sentiment, x = ~Date, y = ~Sentiment,name = 'Sentiment',
             type = 'scatter', mode = 'lines',
             line = list(color = 'rgb(0,100,80)')) %>%
     add_trace(y = ~Sentiment.High, name = 'High Sentiment',  mode = 'lines',
               type = 'scatter',line = list(color = 'transparent'), fill = 'tonexty',
                fillcolor='rgba(0,100,80,0.2)') %>%
     add_trace(y = ~Sentiment.Low, name = 'Low Sentiment', mode = 'lines',
               type = 'scatter', fill = 'tonexty', 
               fillcolor='rgba(0,100,80,0.2)') %>%
    # add_trace(y =~ Sentiment.Low, name = 'Low Sentiment', mode = 'lines') %>%
     layout(title = 'Twitter Sentiment by Month')
p
```

