---
title: "Leaflet Project"
author: "Ryan Jolicoeur"
date: "April 28, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(leaflet)
library(zipcode)
library(readr)

setwd("C:/Users/Ryan/Documents/Data_Science_Studies/Developing Data Products/New_Assignment")

options(scipen=999)

```

## Leaflet Plotting Project
In this project we are going to load zipcode data that has been locally downloaded.
The zip code data includes metrics such as: 

  + Population
  + Timezone
  + City
  + State
  + Zip Code
  + Area Code

In order to place a limit on the zip codes that are read in we will set a threshold of 50,000.  Meaning there will not be any zip codes included that are below a population of 50,000 from our analyzed data set. I also decided to utilize the zipcode package in order to limit the potential incorrect zip formatting I would have.  This package does filtering to: 

  + Insure that all zip codes are 5 digits
  + Include leading 0's if necessary
  + Remove the plus 4 zip code sub indicators if included
```{r Zip_Code_Data}
list.files()
Zip_Data <- read_csv("zip_code_database.csv")

Zip_Data <- Zip_Data %>% 
              filter(irs_estimated_population_2015 > 50000)

Zip_Data$zip   <- clean.zipcodes(Zip_Data$zip)
```

## Leaflet Map

For this step here is where we plot the leaflet dataset.  There are a couple of 
choices that were made in order to analyze the data and to clean the options.  

  + Place popup's on my map to show additional details
  + Utilize the break line option to place multiple items in the popup <br>
  + Add the marker cluster options to true to cluster upon resolution

```{r Map_Data}
Zip_Map <- Zip_Data  %>% 
           leaflet() %>%
            addTiles() %>%
            addMarkers( lng = Zip_Data$longitude, 
                        lat = Zip_Data$latitude,
                        popup = paste("Population 2015:", Zip_Data$irs_estimated_population_2015, "<br>",
                                      "City:", Zip_Data$primary_city, "<br>",
                                      "State:", Zip_Data$state, "<br>",
                                      "Zip:", Zip_Data$zip, "<br>",
                                      "Area_Code:", Zip_Data$area_codes, "<br>",
                                      "Timezone:", Zip_Data$timezone), 
                        clusterOptions = markerClusterOptions())
Zip_Map
```


